Continuous gravitational waves in the lab: recovering audio signals with a table-top optical microphone

### 2020-10-05 paper/ifo-complexAudio.tex
pass through text to edit language in a few places, shortened conclusion, added missing exhibition reference

We describe the additional hardware components required for this demonstration in Section~\ref{sec:photodiode} and initial results in Section~\ref{sec:initialResultsOpMic}. Filter and speech enhancement techniques applied to the data are outlined in Sections~\ref{sec:simple_filters} and~\ref{sec:logmmse}, respectively.
This section is indirectly related to the advanced signal processing techniques required to extract gravitational-wave signals.
In addition to this, the optical microphone serves as an interesting independent demonstration for a broader physics and engineering audience, particularly in undergraduate laboratories.

@@

Audible frequencies are in the range of $\sim 20\,{\rm Hz}$--$20\,{\rm kHz}$. Speech intelligibility requires frequencies up to $3\,{\rm kHz}$ and music requires up to and beyond $8\,{\rm kHz}$~\cite{speech_intelligibility}. Therefore the optical microphone requires a sample rate of at least $16\,{\rm kHz}$ to capture both speech and music. This cannot be achieved with the webcam used in Sections~\ref{sec:single_tone} and ~\ref{sec:viterbi_wandering} as it has a sampling rate of $30\,{\rm Hz}$.
To overcome this issue, we use a photodiode\footnote{A photodiode is an electrical component that acts as a regular diode when no light is incident on it, blocking any current flow in the `reverse' direction. As the intensity of incident light rises, it becomes increasingly conductive in the reverse direction.} at the output of the interferometer to achieve a sampling rate of $16\,{\rm kHz}$.

@@

Sampling any frequency component of the analog signal above the Nyquist frequency of $8\,{\rm kHz}$ leads to aliasing\footnote{folding of higher frequencies above half the sampling rate} into the detected range. We include an anti-aliasing Sallen-Key filter~\cite{sallen_key_filter} tuned to $16\,{\rm kHz}$ before the ADC to prevent this from happening.
This component attenuates any frequencies above $8\,{\rm kHz}$, before they are digitally sampled. We also place a cloth screen over the face of the photodiode to reduce the intensity of the voltage signal as to avoid saturating the ADC.
% It’s not clear what limited the sample rate to 16kHz, but it was likely non-optimal reading of the ADC by the Pi script.
% The ADC used (MCP3008) is quoted at 200kHz (or ksps, kilo samples per second).

@@

%The source audio was played through the speaker with the optical microphone recording for the full duration of the audio (around a minute long for most sources). 
We test the optical microphone with a variety of recordings including speech from different people and music ranging from simple melodies and rhythms to songs. During recordings, care must be taken to minimise activity around the interferometer to reduce the amount of environmental noise coupling into the interferometer. The time series data is then directly converted to a .wav file and played as an audio recording using the \textbf{io.wavfile.write} function. When processing the results, we restrict our analysis to only the first $10\,{\rm s}$ of each observation (for efficiency), and only plot the first second here.

@@

\subsection{A hierarchy of filters}
\label{sec:simple_filters}

@@

Given that we have access to the background noise spectrum, an intuitive way to remove noise is via subtracting the noise spectrum from the recorded spectrum. The fourth panel of Fig.~\ref{fig:noiseSubtract} shows the spectrum obtained after subtracting the background noise spectrum. We see no obvious improvement, which may be attributed to a time-variant noise spectrum. Why the noise sources are time-varying is a fact yet to be determined.

Beyond this naive approach, we need to apply filters to the data.
In signals processing, the ideal filter would be one that:
%\begin{itemize}
i) completely attenuates the undesired parts of the spectrum, 
ii) does not change the rest of the spectrum, and 
iii) smoothly transitions between these regions, as to not damage the time domain signal when seen under convolution. 
%\end{itemize}
However, these three conditions are cannot all hold at once and any filter must compromise between them.

@@

In the above expression, $f_c$ represents the cut-off frequency of the low-pass Butterworth filter, $\varepsilon$ represents the gain, and $n$ is the order of the filter which determines how quickly the response rolls off past the cut-off frequency. Fig.~\ref{fig:butterworth} shows the frequency response of the filter used here, a fifth order ($n = 5$) Butterworth filter with a pass-band of $(150\,{\rm Hz}, 3\,{\rm kHz})$. This high frequency cut-off is chosen since the frequencies important for speech generally lie below $2\,{\rm kHz}$~\cite{speech_intelligibility}.

@@

\subsubsection{Cascade notch filter}

@@

One method to remove mains noise and its harmonics is to use a sequence of notch filters centered at each of the frequency bins we want to remove. This sequence is known as a cascade of notches. Here the notches are smooth in comparison to the naive zeroing of each frequency (which looks like a rectangular comb). The complex frequency response of a typical infinite impulse response (IIR) notch filter can be written as \citep{10.5555/541204}
\begin{equation}
    \label{eqn:notch}
    H(z)=\frac{1+\alpha}{2}\frac{1-2\beta z^{-1}+z^{-2}}{1-\beta(1+\alpha)z^{-1}+\alpha z^{-2}}
\end{equation}
Where $z$ is the complex frequency and $\alpha$ and $\beta$ are parameters that control the filter. $w_0=\cos^{-1}(\beta)$ is the frequency that is completely attenuated (zeroed) at the centre of the notch and $B_w=\cos^{-1}[2\alpha/(1+\alpha^2)]$ is the bandwidth of the notch (which reflects how quickly the response changes around the notched frequency).
We find that a sequence of $15$ notches works well here, with the $k^\mathrm{th}$ notch centred on the $k^\mathrm{th}$ harmonic of the $50\,{\rm Hz}$ mains signal, where $k=0,2,\dots,14$. When then choose the bandwidth and order (here equal to six) of each notch to avoid disturbing useful signals while still allowing for uncertainty in the location of each harmonic of the mains signal. The response of this cascaded notch filter $H(z)$ is the product of the responses of each of the individual $H_k(z)$ notches,
\begin{equation}
    \label{eqn:notch15}
    H(z) = \prod_{k=0}^{14} H_k(z).
\end{equation}

We use the built-in MATLAB filter design toolbox, the (amplitude) response of the first five notch filters is shown in Fig.~\ref{fig:notchMagResponse}. 
The time series and spectrum obtained after applying the cascade notch filter to the speech recording are shown in the third panel of Fig.~\ref{fig:timeNotchWiener} and the first panel of Fig.~\ref{fig:freqNotchWiener}, respectively. We see that the mains harmonics are significantly attenuated in comparison to the results shown in Fig.~\ref{fig:noiseSubtract}.

Although the notch filter removes the mains hum sound (mostly), the filtered recording is not intelligible. Qualitatively it sounds more like a drum than a human voice. Evidently, this is due to loss of voice information under the filter.

\begin{figure*}
\begin{center}
\includegraphics[width=.7\textwidth]{figures/notch_filter_response}
\end{center}
\caption{\label{fig:notchMagResponse}
Magnitude response for the first five notches of the $15$ cascaded notch filter described by Eqns.~\ref{eqn:notch} and ~\ref{eqn:notch15}. 
}
\end{figure*}

@@

A Wiener filter is an advanced statistical technique that estimates the injected signal given prior information about the injected spectrum and the reference spectrum of the background noise. Let the observed noisy speech signal sequence be given as $\mathbf{x}=\{x(0),\dots, x(N-1)\}$, where $N$ is the length of the data sequence. It is the sum of the original injected (or “clean”) signal $\mathbf{s}=\{s(0),\dots,s(N-1)\}$, and the noise sequence $\mathbf{w}=\{w(0),\dots,w(N-1)\}$, 
\begin{equation}
    \mathbf{x}=\mathbf{s}+\mathbf{w}\,.
\end{equation}
Given the observed data $\textbf{x}$, our goal is to make an estimate $\hat{\textbf{s}}$ of the original signal $\textbf{s}$ such that we minimise the (Bayesian) mean square error (MSE), as defined in Eq.~\ref{eq:BMSE}, between the two.
\begin{equation}
\label{eq:BMSE}
\text{BMSE}(\hat{\textbf{s}})=E[(\textbf{s}-\hat{\textbf{s}})^2]\,,
\end{equation}

If we assume that: i) $\textbf{x}$ is wide sense stationary~\footnote{ A random process $\{x(t)\}$ is wide sense stationary (WSS) if for all $t_1,t_2 \in R$, if (1) it’s mean is time invariant, i.e., $\mu_x(t_1)=\mu_x(t_2)=\text{constant}$; and (2) the autocorrelation depends only on the time difference, i.e., $R_x(t_1,t_2)=R_x(\tau),\tau=t_1-t_2$.} with zero mean; ii) the signal $\textbf{s}$ has a mean of zero; and iii) the noise $\textbf{w}$ is uncorrelated with the signal $\textbf{s}$, we can further express $\hat{\textbf{s}}$ to be a linear combination of present and past observed data
\begin{equation}
\hat{{s}}[n]=\sum_{k=0}^{n}h[k]x[n-k]\,,
\end{equation}
where $\textbf{h}=\{h(0),\dots h(n)\}$ represents the coefficients of an $n$th order Wiener filter.
These assumptions are to be justified by the efficacy of the Wiener filter.

%Given the observation data $\mathbf{x}$, our goal is to estimate $\mathbf{s}$ so that the error between $\mathbf{x}$ and the estimate ${\hat{\mathbf{s}}}$ is minimized in the mean square sense,
%\begin{equation}
%    \hat{\mathbf{s}}=\mathop{\arg\min}_{\textbf{s}}||\mathbf{x}-\mathbf{s}||_2^2\,. 
%\end{equation}
%Assuming that $\textbf{x}$ is wide-sense stationary~\footnote{
%A random process $\{x(t)\}$ is wide sense stationary (WSS) if for all
%$t_1,t_2 \in R$, it satisfies (1) mean is time invariant, i.e.,
%$\mu_x(t_1)=\mu_x(t_2)=\text{constant}$; (2) autocorrelation depends
%only on time difference, i.e., $R_x(t_1,t_2)=R_x(\tau),\tau=t_1-t_2$.}
%and that $\textbf{w}$ is stationary and uncorrelated with the signal, we represent the $n$th order Wiener filter by its coefficients $\textbf{h}=\{h(0),\dots(n)\}$.

The famous Wiener-Hopf equation~\citep{noble1959methods} allows us to determine $\textbf{h}$, as\begin{equation}
\label{eqn:wiener-hopf}
\begin{bmatrix}  
r_{xx}[0]&r_{xx}[1]&\dots& r_{xx}[n]\\
r_{xx}[1]&r_{xx}[0]&\dots &r_{xx}[n-1]\\
\vdots&\vdots&\ddots&\vdots\\
r_{xx}[n]&r_{xx}[n-1]&\dots &r_{xx}[0]
\end{bmatrix}
\begin{bmatrix}
h[0]\\
h[1]\\
\vdots\\
h[n]
\end{bmatrix}=
\begin{bmatrix}
r_{ss}[0]\\
r_{ss}[1]\\
\vdots\\
r_{ss}[n]
\end{bmatrix}\,,
\end{equation}
where $r_{xx}$ and $r_{ss}$ are the auto-correlation functions of $\mathbf{x}$ and $\mathbf{s}$ between timestep $i$ and $i+n$, 
%\begin{equation*}
%\left\{ 
\begin{eqnarray} 
r_{xx}[n] &~=~& E[x(i)~x(i+n)] \,,\\
r_{ss}[n] &~=~& E[s(i)~s(i+n)] \,.
%r_{xx}[n] &=& E[x(i)\, &x(i+n)] \\ 
%r_{ss}[n] &=& E[s(i)\, &s(i+n)] 
\end{eqnarray} 
%\right\}  
%\end{equation*}
%where $r_{xx}$ and $r_{ss}$ is the auto-correlation function of $x$ and $s$.

As an instructive aside, if we let the Wiener filter be non-causal (i.e. we estimate the current signal based on both past \emph{and future} observations), then we can represent Eqn.~\ref{eqn:wiener-hopf} in the frequency domain as
\begin{equation}
\label{eqn:wiener}
    H(f)=\frac{P_{ss}(f)}{P_{xx}(f)}=\frac{P_{ss}(f)}{P_{ss}(f)+P_{ww}(f)}
\end{equation}
where $P_{xx}(f), P_{ss}(f), P_{ww}(f)$ are the spectra of the observed noisy data (i.e., signal + noise), the injected signal, and the background noise, respectively. Intuitively, from Eqn.~\ref{eqn:wiener}, we can see that the non-causal Wiener filter amplifies the input signal where the signal to noise ratio (SNR) is high, and attenuates the signal where the SNR is low. The causal Wiener filter (that only makes estimates based on past observations) is similar. More detailed analysis of both kinds of Wiener filters can be found in Ref.~\citep{10.5555/151045}.
% That this filter is non-causal makes it unsuitable for real time signal processing

@@

What we’re attempting here is not new, speech enhancement of noisy channels is a classic problem in signal processing. To borrow from that field, Yi Hu and P.C. Loizon~\cite{SubjectiveComparison} compared $13$ speech enhancement methods and found the log minimum means-square error (logMMSE) estimator to be the best among them, qualitatively, at recovering speech. This estimator is based on speech enhancement techniques discussed in Ref.~\cite{Ephraim1984SpeechEU_logMMSE} and minimises the mean square error (MSE) of the estimate from the injected signal, like the Wiener filter above, except that is measures the MSE between the logarithm of the Fourier amplitudes. This is motivated by the fact that the logarithm approximates the response of the human ear~\cite{SubjectiveComparison}. We apply an existing implementation of the logMMSE estimator (see Ref.~\cite{logmmse}) to the recorded signal.
%Hu~\&~Loizou~(2006)~\cite{SubjectiveComparison} compare 13 speech enhancement methods and find the best to be a log minimum mean-square error (log-MMSE) estimator. 
%This type of estimator is based on work Ephraim~\&~Malah~(1984)~\cite{Ephraim1984SpeechEU_logMMSE} into speech enhancement by minimising the mean square error (MSE) to the logarithm of the spectral (Fourier) amplitude.

@@

The results of the logMMSE estimator are shown in Figs.~\ref{fig:logMMSE_timeseries} and~\ref{fig:logMMSE_spectrum}. The top two panels of each figure show the original speech signal and anti-aliased reading from the optical microphone for ease of comparison. The third panel of Figs.~\ref{fig:logMMSE_timeseries} and~\ref{fig:logMMSE_spectrum} show the time series and corresponding spectral amplitude after applying the logMMSE estimator. We see significant attenuation of the mains harmonics as well as a general smoothing of the spectrum. The logMMSE method indeed removes most of the background noise, but does not significantly enhance the speech as the voice sounds muffled and indistinct, with the words unable to be understood.

We find some improvement with music over speech. After applying the logMMSE estimator, simple chords and drums can be heard clearly, however more composite sounds and complex melodies cannot be heard clearly. Our observations suggest that this is especially true for instruments of certain timbres (harmonic profiles), in particular flutes and violins sometimes can’t be heard at all. This could be a perceptual effect or a frequency dependence somewhere in the optical microphone, although the exact cause is yet to be determined. Speculating, perhaps the speaker-mirror coupling is stronger at low frequencies and thus instruments like electric bass and drums are louder in the results.

To address these problems, we need to determine whether the signals that are audibly missing (the diction in the speech and complex melodies in music) are indeed being transmitted through the optical microphone at all. Or if instead they are present in the noisy data but we need better techniques to extract them. To determine this requires a better understanding of the system as discussed in Section~\ref{sec:future_work}.

>>>>

We describe the additional hardware components required for this demonstration in Section~\ref{sec:photodiode} and initial results in Section~\ref{sec:initialResultsOpMic}. Filter and speech enhancement techniques applied to the data are outlined in Section~\ref{sec:filters}.
This section is indirectly related to the advanced signal processing techniques required to extract gravitational-wave signals.
In addition to this, the optical microphone serves as an interesting independent demonstration for a broader physics and engineering audience, particularly in undergraduate laboratories.

@@

Audible frequencies are in the range of $\sim 20\,{\rm Hz}$--$20\,{\rm kHz}$. Speech intelligibility requires frequencies up to $3\,{\rm kHz}$ and music requires up to and beyond $8\,{\rm kHz}$~\cite{speech_intelligibility}. Therefore the optical microphone requires a sample rate of at least $16\,{\rm kHz}$ to capture both speech and music. This cannot be achieved with the webcam used in Sections~\ref{sec:single_tone} and ~\ref{sec:viterbi_wandering} as it has a sampling rate of $30\,{\rm Hz}$.
To overcome this issue, we use a photodiode\footnote{A photodiode is an electrical component that acts as a regular diode when no light is incident on it, blocking any current flow in the reverse direction. As the intensity of incident light rises, it becomes increasingly conductive in the reverse direction.} at the output of the interferometer to achieve a sampling rate of $16\,{\rm kHz}$.

@@

Sampling any frequency component of the analog signal above the Nyquist frequency of $8\,{\rm kHz}$ leads to aliasing\footnote{Folding of frequencies greater than half the sampling rate.} into the detected range. We include an anti-aliasing Sallen-Key filter~\cite{sallen_key_filter} tuned to $16\,{\rm kHz}$ before the ADC to prevent this from happening.
This component attenuates any frequencies above $8\,{\rm kHz}$, before they are digitally sampled. We also place a cloth screen over the face of the photodiode to reduce the intensity of the voltage signal and avoid saturating the ADC.
% It’s not clear what limited the sample rate to 16kHz, but it was likely non-optimal reading of the ADC by the Pi script.
% The ADC used (MCP3008) is quoted at 200kHz (or ksps, kilo samples per second).

@@

%The source audio was played through the speaker with the optical microphone recording for the full duration of the audio (around a minute long for most sources). 
We test the optical microphone with a variety of recordings including speech from different people and music ranging from simple melodies and rhythms to songs. During recordings, care is taken to minimise activity around the demonstration to reduce the amount of environmental noise coupling into the interferometer. The time series data is then directly converted to a .wav file and played as an audio recording using the \textbf{io.wavfile.write} function. When processing the results, we restrict our analysis to only the first $10\,{\rm s}$ of each observation (for efficiency), and only plot the first second here.

@@

\subsection{A hierarchy of filters}
\label{sec:filters}

@@

Given that we have access to the background noise spectrum, an intuitive way to remove noise is via subtracting the noise spectrum from the recorded spectrum. The fourth panel of Fig.~\ref{fig:noiseSubtract} shows the spectrum obtained after subtracting the background noise spectrum. We see no obvious improvement, which may be attributed to a time-variant noise spectrum the cause of which is unidentified. %Why the noise sources are time-varying is a fact yet to be determined.

Beyond this naive approach, we apply a range of filters to the data.
In signals processing, the ideal filter would be one that:
%\begin{itemize}
i) completely attenuates the undesired parts of the spectrum, 
ii) does not change the rest of the spectrum, and 
iii) smoothly transitions between these regions, as to not damage the time domain signal when seen under convolution. 
%\end{itemize}
However, these three conditions are cannot all hold at once and any filter must compromise between them.

@@

In the above expression, $f_c$ represents the cut-off frequency of the low-pass Butterworth filter, $\varepsilon$ represents the gain, and $n$ is the order of the filter which determines how quickly the response rolls off past the cut-off frequency. Fig.~\ref{fig:butterworth} shows the frequency response of the filter used here, a fifth order ($n = 5$) Butterworth filter with a pass-band of $(150\,{\rm Hz}$, $3\,{\rm kHz})$. This high frequency cut-off is chosen since the frequencies important for speech generally lie below $2\,{\rm kHz}$~\cite{speech_intelligibility}.

@@

\subsubsection{Cascade notch filter}
\begin{figure*}
\begin{center}
\includegraphics[width=.9\textwidth]{figures/notch_filter_response}
\end{center}
\caption{\label{fig:notchMagResponse}
Magnitude response for the first five notches of the $15$ cascaded notch filter described by Eqns.~\ref{eqn:notch} and ~\ref{eqn:notch15}. 
}
\end{figure*}

One method to remove mains noise and its harmonics is to use a sequence of notch filters centred at each of the frequency bins we want to remove. This sequence is known as a cascade of notches. Here the notches are smooth in comparison to the naive zeroing of each frequency (which looks like a rectangular comb). The complex frequency response of a typical infinite impulse response (IIR) notch filter can be written as \citep{10.5555/541204}
\begin{equation}
    \label{eqn:notch}
    H(z)=\frac{1+\alpha}{2}\frac{1-2\beta z^{-1}+z^{-2}}{1-\beta(1+\alpha)z^{-1}+\alpha z^{-2}}
\end{equation}
Where $z$ is the complex frequency and $\alpha$ and $\beta$ are parameters that control the filter. $w_0=\cos^{-1}(\beta)$ is the frequency that is completely attenuated (zeroed) at the centre of the notch and $B_w=\cos^{-1}[2\alpha/(1+\alpha^2)]$ is the bandwidth of the notch (which reflects how quickly the response changes around the notched frequency).
We find that a sequence of $15$ notches works well here, with the $k^\mathrm{th}$ notch centred on the $k^\mathrm{th}$ harmonic of the $50\,{\rm Hz}$ mains signal, where $k=0,2,\dots,14$. When then choose the bandwidth and order (here equal to six) of each notch to avoid disturbing useful signals while still allowing for uncertainty in the location of each harmonic of the mains signal. The response of this cascaded notch filter $H(z)$ is the product of the responses of each of the individual $H_k(z)$ notches,
\begin{equation}
    \label{eqn:notch15}
    H(z) = \prod_{k=0}^{14} H_k(z).
\end{equation}

We use the built-in MATLAB filter design toolbox in this work. 
The amplitude response of the first five notch filters is shown in Fig.~\ref{fig:notchMagResponse}. 
The time series and spectrum obtained after applying the cascade notch filter to the speech recording are shown in the third panel of Fig.~\ref{fig:timeNotchWiener} and the first panel of Fig.~\ref{fig:freqNotchWiener}, respectively. We see that the mains harmonics are significantly attenuated in comparison to the results shown in Fig.~\ref{fig:noiseSubtract}.

Although the notch filter removes much of the mains hum sound, the filtered recording is not intelligible. Qualitatively it sounds more like a drum than a human voice. Evidently, this is due to loss of voice information under the filter.

@@

@@

A Wiener filter is an advanced statistical technique that estimates the injected signal given prior information about the injected spectrum and the reference spectrum of the background noise. Let the observed noisy speech signal sequence be given as $\mathbf{x}=\{x(0),\dots, x(N-1)\}$, where $N$ is the length of the data sequence. It is the sum of the original injected signal $\mathbf{s}=\{s(0),\dots,s(N-1)\}$, and the noise sequence $\mathbf{w}=\{w(0),\dots,w(N-1)\}$, 
\begin{equation}
    \mathbf{x}=\mathbf{s}+\mathbf{w}\,.
\end{equation}
Given the observed data $\textbf{x}$, our goal is to make an estimate $\hat{\textbf{s}}$ of the original signal $\textbf{s}$ such that we minimise the (Bayesian) mean square error (MSE), as defined in Eq.~\ref{eq:BMSE}, between the two.
\begin{equation}
\label{eq:BMSE}
\text{BMSE}(\hat{\textbf{s}})=E[(\textbf{s}-\hat{\textbf{s}})^2]\,,
\end{equation}

If we assume that: i) $\textbf{x}$ is wide sense stationary~\footnote{ A random process $\{x(t)\}$ is wide sense stationary if, for all $t_1,t_2 \in R$, if (1) its mean is time invariant, i.e., $\mu_x(t_1)=\mu_x(t_2)=\text{constant}$; and (2) the autocorrelation depends only on the time difference, i.e., $R_x(t_1,t_2)=R_x(\tau),\tau=t_1-t_2$.} with zero mean; ii) the signal $\textbf{s}$ has a mean of zero; and iii) the noise $\textbf{w}$ is uncorrelated with the signal $\textbf{s}$, we can further express $\hat{\textbf{s}}$ to be a linear combination of present and past observed data
\begin{equation}
\hat{{s}}[n]=\sum_{k=0}^{n}h[k]x[n-k]\,,
\end{equation}
where $\textbf{h}=\{h(0),\dots h(n)\}$ represents the coefficients of an $n$th order Wiener filter.
% What this sentence is trying to convey is not clear to me
%These assumptions are to be justified by the efficacy of the Wiener filter.
%Given the observation data $\mathbf{x}$, our goal is to estimate $\mathbf{s}$ so that the error between $\mathbf{x}$ and the estimate ${\hat{\mathbf{s}}}$ is minimized in the mean square sense,
%\begin{equation}
%    \hat{\mathbf{s}}=\mathop{\arg\min}_{\textbf{s}}||\mathbf{x}-\mathbf{s}||_2^2\,. 
%\end{equation}
%Assuming that $\textbf{x}$ is wide-sense stationary~\footnote{
%A random process $\{x(t)\}$ is wide sense stationary (WSS) if for all
%$t_1,t_2 \in R$, it satisfies (1) mean is time invariant, i.e.,
%$\mu_x(t_1)=\mu_x(t_2)=\text{constant}$; (2) autocorrelation depends
%only on time difference, i.e., $R_x(t_1,t_2)=R_x(\tau),\tau=t_1-t_2$.}
%and that $\textbf{w}$ is stationary and uncorrelated with the signal, we represent the $n$th order Wiener filter by its coefficients $\textbf{h}=\{h(0),\dots(n)\}$. 
The famous Wiener-Hopf equation~\citep{noble1959methods} allows us to determine $\textbf{h}$, as\begin{equation}
\label{eqn:wiener-hopf}
\begin{bmatrix}  
r_{xx}[0]&r_{xx}[1]&\dots& r_{xx}[n]\\
r_{xx}[1]&r_{xx}[0]&\dots &r_{xx}[n-1]\\
\vdots&\vdots&\ddots&\vdots\\
r_{xx}[n]&r_{xx}[n-1]&\dots &r_{xx}[0]
\end{bmatrix}
\begin{bmatrix}
h[0]\\
h[1]\\
\vdots\\
h[n]
\end{bmatrix}=
\begin{bmatrix}
r_{ss}[0]\\
r_{ss}[1]\\
\vdots\\
r_{ss}[n]
\end{bmatrix}\,,
\end{equation}
where $r_{xx}$ and $r_{ss}$ are the auto-correlation functions of $\mathbf{x}$ and $\mathbf{s}$ between timestep $i$ and $i+n$, 
%\begin{equation*}
%\left\{ 
\begin{eqnarray} 
r_{xx}[n] &~=~& E[x(i)~x(i+n)] \,,\\
r_{ss}[n] &~=~& E[s(i)~s(i+n)] \,.
%r_{xx}[n] &=& E[x(i)\, &x(i+n)] \\ 
%r_{ss}[n] &=& E[s(i)\, &s(i+n)] 
\end{eqnarray} 
%\right\}  
%\end{equation*}
%where $r_{xx}$ and $r_{ss}$ is the auto-correlation function of $x$ and $s$.

%As an instructive aside, i
If we let the Wiener filter be non-causal (i.e. we estimate the current signal based on both past \emph{and future} observations), then we can represent Eqn.~\ref{eqn:wiener-hopf} in the frequency domain as
\begin{equation}
\label{eqn:wiener}
    H(f)=\frac{P_{ss}(f)}{P_{xx}(f)}=\frac{P_{ss}(f)}{P_{ss}(f)+P_{ww}(f)}
\end{equation}
where $P_{xx}(f), P_{ss}(f), P_{ww}(f)$ are the spectra of the observed noisy data, the injected signal, and the background noise, respectively. Intuitively, from Eqn.~\ref{eqn:wiener}, we can see that the non-causal Wiener filter amplifies the input signal where the signal to noise ratio (SNR) is high, and attenuates the signal where the SNR is low. The causal Wiener filter (that only makes estimates based on past observations) is similar. More detailed analysis of both kinds of Wiener filters can be found in Ref.~\citep{10.5555/151045}.
% That this filter is non-causal makes it unsuitable for real time signal processing

@@

%probably a bit too causal language 
%What we’re attempting here is not new, 
Speech enhancement of noisy channels is a classic problem in signal processing. 
% shouldn't we make the citations consistent throughout? We don't mention author names up to this point and typically journals have a set style guide. - Hannah 
%To borrow from that field, Yi Hu and P.C. Loizon~\cite{SubjectiveComparison} compared $13$ speech enhancement methods and found the log minimum means-square error (logMMSE) estimator to be the best among them, qualitatively, at recovering speech. 
In Ref.~\cite{SubjectiveComparison} a comparison is made of $13$ speech enhancement methods, finding the log minimum means-square error (logMMSE) estimator to be the best, qualitatively, at recovering speech. 
This estimator is based on speech enhancement techniques discussed in Ref.~\cite{Ephraim1984SpeechEU_logMMSE} and minimises the mean square error (MSE) of the estimate from the injected signal, like the Wiener filter above, except that is measures the MSE between the logarithm of the Fourier amplitudes. This is motivated by the fact that the logarithm approximates the response of the human ear~\cite{SubjectiveComparison}. We apply an existing implementation of the logMMSE estimator (see Ref.~\cite{logmmse}) to the recorded signal.
%Hu~\&~Loizou~(2006)~\cite{SubjectiveComparison} compare 13 speech enhancement methods and find the best to be a log minimum mean-square error (log-MMSE) estimator. 
%This type of estimator is based on work Ephraim~\&~Malah~(1984)~\cite{Ephraim1984SpeechEU_logMMSE} into speech enhancement by minimising the mean square error (MSE) to the logarithm of the spectral (Fourier) amplitude.

@@

The results of the logMMSE estimator are shown in Figs.~\ref{fig:logMMSE_timeseries} and~\ref{fig:logMMSE_spectrum}. The top two panels of each figure show the original speech signal and anti-aliased reading from the optical microphone for ease of comparison. The third panel of Figs.~\ref{fig:logMMSE_timeseries} and~\ref{fig:logMMSE_spectrum} show the time series and corresponding spectral amplitude respectively after applying the logMMSE estimator. We see significant attenuation of the mains harmonics as well as a general smoothing of the spectrum. The logMMSE method indeed removes most of the background noise, but does not significantly enhance the speech as the voice sounds muffled and indistinct.
% suggest remove as it's just rephrasing what's already been said
%, with the words unable to be understood.

We find some improvement with music over speech. After applying the logMMSE estimator, simple chords and drums can be heard, however more composite sounds and complex melodies cannot be heard clearly. Our observations suggest that this is especially true for instruments of certain timbres (harmonic profiles), in particular flutes and violins sometimes can’t be heard at all. This could be a perceptual effect or a frequency dependence somewhere in the optical microphone.
%, although the exact cause is yet to be determined.  - repetition
Speculating, perhaps the speaker-mirror coupling is stronger at low frequencies and thus instruments like electric bass and drums are louder in the results.

To address these problems, we need to determine whether the signals that are audibly missing (the diction in the speech and complex melodies in music) are indeed being transmitted through the optical microphone at all. 
%Or if instead they are present in the noisy data but we need better techniques to extract them. - should probably justify what you mean by better if you are going to say it here, but I think enough is discussed in section VI for it not to be necessary here - hannah 
To determine this requires a better understanding of the system as discussed in Section~\ref{sec:future_work}.
